%-------------------------
% Resume in Latex
% Author : Dhananjaya D R
% Website: https://github.com/dhananjayadr/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://dhananjayadr.vercel.app}{\Large Dhananjaya D R}} & Email: \href{mailto:vishwasdhananjaya@gmail.com}{vishwasdhananjaya@gmail.com}\\
  \href{https://dhananjayadr.vercel.app}{https://dhananjayadr.vercel.app} & Mobile: +91-9108869298 \\
\end{tabular*}


%-----------PROGRAMMING SKILLS-----------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Python, Bash, Javascript}
     }
    \item {
    \textbf{Technologies}{: Flask, Sitespeed, K6, Linux, Git, Selenium, Playwright, Postman, Jenkins, MongoDB, AWS}
   }
 \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

\resumeSubheading
    {Tekion}{Bengaluru}
    {Senior Performance Engineer}{Sep 2020 - Present}
    \resumeItemListStart
      \resumeItem{Tool Development}
        {Developed tools for internal teams to visualize system performance:
        \begin{itemize}
          \item \textbf{Browser Plugin}: Generates a Sitespeed script based on user actions for UI performance testing.
          \item \textbf{Python Package}: Converts Postman collections into K6 scripts for load testing, targeted at development teams.
          \item \textbf{ttest}: Ensures mathematical reliability of performance tests by checking statistical accuracy.

        \end{itemize}}
      \resumeItem{Framework Development}
        {Designed and implemented frameworks for automation testing:
        \begin{itemize}
          \item \textbf{Hardware Testing Framework}: Built embedded device testing framework using Python and Bash. Supports any IoT device with SSH or serial port connections.
          \item \textbf{Web Testing Framework}: Created using Python, Selenium, Pytest, and Bash for web application testing.
          \item \textbf{Android Application Testing Framework}: Developed using Node.js with a simulated backend for local testing.
        \end{itemize}}
      \resumeItem{Scripting}
        {Extensive experience in programming and scripting with Python, Bash, and JavaScript, primarily on Unix like OS. Mostly Automated recurring tasks those exceeding 30 seconds.}
    \resumeItemListEnd

      \resumeSubheading
      {Fubeus}{Remote}
      {Software Engineer-Test}{Jul 2019 - Aug 2019}
      \resumeItemListStart
             \item
             {Developed a Jenkins integrated dashboard to execute automation jobs across 1,500 machines set up in KVM for testing CPU thermal tools and display results.}
            \item
            {Refactored and optimized an existing Python automation codebase and Bash scripts to improve performance and maintainability.}
      \resumeItemListEnd

    \resumeSubheading
      {Atomiton}{Bengaluru}
      {Software Engineer}{Oct 2019 - May 2020}
      \resumeItemListStart
             \item
              {Responsible for test estimation, reporting, and automation test case development for a web application.}
             \item
              {Conducted data analysis, visualization, and processing of unstructured IO profile data for real time workloads using Python.}
             \item
              {Set up and maintained version control using GIT for automation framework development. And configured Jenkins for CI with Bitbucket and automated email monitoring systems.}
      \resumeItemListEnd

      %   \resumeSubheading
      % {Sri Ramakrishna Math Chennai}{Chennai}
      % {volunteer as Development Engineer}{Feb 2019 - Oct 2019}
      % \resumeItemListStart
      %   \item{ I set up the framework for internal communication, including motion, vision, and  voice, for the robot we were building. I also designed robot parts and printing them on a 3D printer.}
      %   \item{Python backend for a web application used by librarians at the math to manager library operations.}
      % \resumeItemListEnd

    \resumeSubheading
      {DiFACTO Robotics and Automation}{Bengaluru}
      {Development Engineer}{Jun 2017 - Jan 2019}
      \resumeItemListStart
        \item
        {Programmed industrial robots for applications ranging from production lines to the medical applications.}
        \item
        {Developed a Python application to identify defective objects in real time and classify them.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
  \resumeSubItem{Volunteer (Feb 2019 - Oct 2019)}
    {Volunteered at Sri Ramakrishna Math, Chennai, where I set up the communication framework for a robot project and a Developed Python based website to manage library operations.}
    \resumeSubItem{heatmap}
      {A browser plugin that highlights page elements based on their performance metrics.}
    \resumeSubItem{latency}
      {A Bash script that measures the latency between your machine and various AWS regions.}
    \resumeSubItem{bmeter}
      {An attempt to create a plugin manager for Apache JMeter using bash scripting.}
  \resumeSubHeadingListEnd
% \vspace{1mm}
%   \small{All source code is available on my \textbf{\href{https://github.com/dhananjayadr}{GitHub account}} and is public.}
%
%--------EDUCATION------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University Visvesvaraya College of Engineering}{Bengaluru}
      {Bachelor of Engineering in Mechanical engineering;  Pct.: 72.5\%}{Aug 2013 -- July 2017}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}